
\documentclass{report}
% \documentclass[runningheads,12pt]{llncs}
\input{preamble}

\title{HMLV-survey}
\author{Malthe Birkebæk, Mikkel Ejsing, Marting Braas}
\date{}

\begin{document}


% -------- FRONT MATTER -------- 
\pagenumbering{roman}
\thispagestyle{empty}
\maketitle


\newpage
\pagestyle{plain}

\tableofcontents 
\input{misc/acronyms.tex}

% -------- MAIN MATTER -------- 
\newpage
\pagenumbering{arabic}

% Activate fancyhdr with Page X of Y in footer
\pagestyle{fancy}
\fancyhf{}  % clear all headers and footers
\fancyfoot[C]{Page \thepage\ of \pageref*{LastPage}}
\renewcommand{\headrulewidth}{0pt}  % no header line

\chapter{Introduction}
\input{chapters/introduction}

\chapter{Methodology}
\input{chapters/methodology}

\chapter{Industry 3.0} \label{chap:industry3.0}
% Industry 3.0 is a single tex file chapter
\input{chapters/Indsutry3.0/Industry3.0}

\chapter{Industry 4.0}

Some key technologies to consider touching upon in this section (/suggested structure):
\begin{itemize}
    \item Cyper-Physical Systems: Concept, implementations, impact on \ac{hmlv}.
    \item \ac{iot} \& Industrial Connectivity: Sensor networks, OPC UA, data pipelines.
    \item Big Data \& Analytics: Predictive maintenance, real-time monitoring.
    \item Automation \& Robotics: Reconfigurable automation, co-bots, flexible robotic cells.
    \item AI/ML for Decision Support: Anomaly detection, predictive scheduling, adaptive control.
    \item MLOps in Manufacturing: Deployment challenges (real-time, PLC integration).
    \item Cloud \& Edge Computing: architectures for \ac{hmlv} environments.
\end{itemize}

\input{chapters/Industry4.0/CPS}
\input{chapters/Industry4.0/IOT}
\input{chapters/Industry4.0/Big_data}
\input{chapters/Industry4.0/Automation}
\input{chapters/Industry4.0/Decision_support}
\input{chapters/Industry4.0/MLops}
\input{chapters/Industry4.0/cloud_and_edge_computing}

\chapter{Industry 5.0}

Some key technologies to consider touching upon in this section (/suggested structure):
\begin{itemize}
    \item Digital Twins: Simulation, prediction, continuous synchronization.
    \item Human-Centricity: Operators in the loop, augmented decision support.
    \item Resilience \& Adaptability: Handling disruptions, supply chain integration.
    \item Sustainability \& Circularity: Energy efficiency, material reuse.
    \item Trustworthy AI \& Explainability: Operators must trust AI outputs.
    \item Collaborative Robotics: Cobots with human oversight.
\end{itemize}

\input{chapters/Industry5.0/digital-twins}
\input{chapters/Industry5.0/human-centric}
\input{chapters/Industry5.0/resilience-and-adaptibility}
\input{chapters/Industry5.0/sustainability-and-circularity}
\input{chapters/Industry5.0/ethics-and-trustworthy-ai}
\input{chapters/Industry5.0/co-bots}


\chapter{Conclusion}
\input{conclusion}

% -------- END MATTER -------- 
\newpage
% \printbibliography
\bibliographystyle{IEEEtran}
\bibliography{references} 

% \label{LastPage}
\end{document}
