\section{Terminology}
This section outlines some of the terminology common to the manifacturing industry, with a particular focus on \ac{hmlv}. 
Readers with more experience in the field can easily skip this section.

\subsubsection{Shop Floor}
The physical area where production takes place.
It includes machines, workstations, material handling systems, and personnel.
In \ac{hmlv}, the shop floor is often highly flexible and dynamic due to frequent changes in production orders.

\subsubsection{Line}
A sequence of machines or workstations through which a product moves during manufacturing.
Lines can be dedicated to a single product (low-mix) or reconfigurable to handle multiple products (high-mix).

\subsubsection{Cell}
A cell is a group of machines, workstations, and operators arranged together to complete a set of related operations or produce a family of products.
The idea is to create a self-contained mini-production unit within the shop floor.

\subsubsection{Process}
A set of operations or steps required to transform raw materials or components into a finished product.
Processes can be discrete (individual steps) or continuous (ongoing production).

\subsubsection{Unit}
A single instance of a product being manufactured.
In \ac{hmlv}, units are often produced in small batches, and each unit may have unique specifications.

\subsubsection{Batch}
A collection of units processed together, common in low-volume settings.

\subsubsection{Job / Order}
A customer request specifying product, quantity, and delivery time.

\subsubsection{Setup / Changeover}
The process of preparing a machine or line to produce a different product, often a focus in \ac{hmlv} manufacturing.

\subsubsection{Component}
A part or subassembly that is used to build a unit.
Components may come from internal production or external suppliers.

\subsubsection{Property}
A measurable characteristic of a unit, component, or process, such as dimensions, material hardness, or temperature during processing.

\subsubsection{Device}
A device is typically also refered to as an edge node, and is any type of electronic device that can measure some property and transmit these values via communication protocols.

\subsubsection{Event}
A discrete occurrence on the shop floor, such as the start or end of a process, a machine failure, or an inspection.

