\section{Human Centric}\label{sec:human-centric}
A key distinction between Industry 4.0 and Industry 5.0 is the inclusion of the human as a central part of the manufacturing process.
While Industry 4.0 emphasizes mass production, mass productivity, and performance through automation, often to eliminate or minimize the need for human interventions,
industry 5.0, takes a human-centric approach, striving to achieve the most effective collaboration between humans and machines or robots, with the humans well-being in focus.
In this paradigm, robots and automated systems are assigned with repetitive and labor-intensive tasks, whereas humans serves as decision makers contributing with critical thinking, creativity, problem-solving skills and their innovative mindset cite{https://www.sciencedirect.com/science/article/pii/S2452414X21000558}.
Such collaboration is particularly valuable in complex tasks and non-routine tasks, that are not easily automated.
cite{Industry 5.0: A survey on enabling technologies and potential applications}.
In \ac{hmlv}, this human-centric approach allows for better adaptability and flexibility to product variations and disruptions.


%Paper der skal læses:
%- Industry 5.0: A survey on enabling technologies and potential applications
%- A Literature Review of the Challenges and Opportunities of the Transition from Industry 4.0 to Society 5.0 
%- Industry 5.0 in Manufacturing: Enhancing Resilience and Responsibility through AI-Driven Predictive Maintenance, Quality Control, and Supply Chain Optimization
%- Digital Twins for Industry 5.0: Unlocking the Human Potential (Genlæs)
%- A Digital Twin Driven Human-Centric Ecosystem for Industry 5.0 (Genlæs)
%- Intelligent Manufacturing From the Perspective of Industry 5.0: Application Review and Prospects
%- Human–machine interaction towards Industry 5.0: Human-centric smart manufacturing

\subsection{Enabling technologies}
To enable a human-centric approach, several technologies can be utilized, including collaborative robots \ac{Co-bots}, \ac{AI}, \ac{ML}, Human Machine Interface \ac{HMI}, \ac{XR}, and \ac{DT}.
Co-bots in industrial settings are developed to collaborate with factory workers, assisting them and alleviating them from repetitive tasks, while ensuring a safe and productive environment.
Moreover, \ac{AI} and \ac{ML} can be employed for decision making, by supporting applications such as with predictive maintenance, quality control, and supply chain optimization.


% A bit about the Human Machine Interaction and Extended Reality (XR).
\ac{HMI} plays an important role in enabling human understanding and interaction with machinery in manufacturing settings. 
Through \ac{HMI}s, operators can see the current state of the machine, and see real-time information about performance and production status.
Beyond 2D screens, other enabling technologies such as: Extended Reality \ac{XR} technologies, such as Virtual Reality \ac{VR}, Augmented Reality \ac{AR}, 
and Mixed Reality \ac{MR} present a more immersive way for humans to interact with machines.
These technologies can be used by the operator in various contexts, including production line monitoring, remote assisting, virtual assembly and 
maintenance instructions, navigation inside and outside the manufacturing facility and training of new employees/operators.
\cite{en15176276}. %-  A Literature Review of the Challenges and Opportunities of the Transition from Industry 4.0 to Society 5.0
In \cite{CHOI2022102258} they demonstrate how safety in human–machine interaction can be enhanced using \ac{AR}, digital twins, and \ac{AI}.
They propose an integrated mixed reality system for safety-aware human–robot collaboration, where \ac{DL} and \ac{DT} track workspace safety and assist operators in real time through smart MR glasses.

%- Co-bots: Human robot collaboration
%- Artificial Intelligence (AI) and Machine Learning (ML): Decision support, predictive maintenance, quality control, and supply chain optimization.
%- Human Machine Interface (HMI): enables effective communication and interaction between humans and machines/robots.
%- Extended Reality (XR): Virtual Reality(VR), Augmented Reality (AR), and Mixed Reality (MR). Help the operator in monitoring of the production line, new employee/operator training, assembly and maintenance instructions, and support. 
%- Digital Twins: Enable Decision Support, and Human/Machine Digital Twins collaboration.
%- Cobots: Collaborative robots designed to work alongside humans.

