Some key technologies to consider touching upon in this section:
\begin{itemize}
  \item Automation \& IT systems \ac{plc}, \ac{cnc}, \ac{mes}, \ac{erp}.
  \item Lean manufacturing, \ac{oee}, \ac{spc}, Layout/flow optimization.
    \item Operations research in scheduling.
    \item Limitations for \ac{hmlv} (rigidity, poor adaptability).
\end{itemize}

\section{Overall Equipment Effectiveness}\label{sec:oee}
One of the most fundamental metrics in industrial manufacturing is \ac{oee}. 
It is a metric that provides insights into the total throughput of individual production devices.
The \ac{oee} is calculated as a product of three percentage factors: availability, performance, and quality:
\[
\text{OEE} = \text{Availability} \times \text{Performance} \times \text{Quality}
\]
The availability measures the percentage of time during which the machine is available for executing tasks.
Whenever the machine stops, its availability decreases.
High availability is achieved when there is minimal downtime.
\[
\text{Availability} = \frac{\text{Total Operation Time} - \text{Total Downtime}}{\text{Total Operation Time}}
\]
Performance is the ratio between the actual and ideal number of produced units during uptime.
High performance is achieved when the actual cycle time is close to the ideal cycle time.
The ideal cycle time is typically provided by the machine manufacturer.
\[
\text{Performance} = \frac{\text{Ideal Cycle Time} \times \text{Total Units Produced}}{\text{Total Operation Time} - \text{Total Downtime}}
\]
The quality is calculated as the number of good units divided by the total number of produced units.
If a large number of units produced by the machine are discarded, the Quality will be lowered.
\[
\text{Quality} = \frac{\text{Good Units}}{\text{Total Units Produced}}
\]

\section{PackML State}

\section{Simulation and Scheduling}\label{sec:simulation-and-scheduling}

\section{SPC}\label{sec:spc}

\section{Lean Manufacturing}\label{sec:lean-manufacturing}

\section{Product Line Design / Group Technology}\label{sec:product-line-design}

\section{Layout and Flow Optimization}\label{sec:layout-and-flow-optimization}
